Draft: Notes on the revised Hidden weight function

### 2024-08-02 RevisedHiddenWeight.tex

Another immediate case for zero coefficients is the following:
\begin{Prop}
    If $p=q$ and $k$ is odd, then $\Dnka nka=0$.
\end{Prop}

\begin{proof}
    If $p=q$, we have $P_a(z)=(z^4-6z^2+1)^p(z^2+1)^r$, which can be seen as a polynomial in $z^2$. Thus, the coefficient $\Dnka nka$ of $z^k$ for odd $k$ must be zero in $P_a(z)$.
\end{proof}

@@

@@

\begin{remark}
    We can even go ahead and choose $R=R_{n,k}$ in terms of $n$ and $k$, in such a way that the upper bound of $B_{R,n,k}=(M_R)^{n/2}/R^k$ is minimized. To do this, consider any $1\leq k\leq n-1$. We can actually assume that $k\leq n/2$: if $k>n/2$, replace it by $n-k$ (recall that $|\Dnka nka|=|\Dnka n{n-k}a|$ by Property \ref{prop:symmetry}). One can show that $B_{R,n,k}$ is minimal for the following choice of $R=R_{n,k}$:
    \[
        R_{n,k}=\begin{cases}
            \frac{n-2k-\sqrt{2(n-2k)^2-n^2}}{2(n-k)}&\text{if $k\leq\frac{2-\sqrt 2}{4}\cdot n$}\\
            \sqrt{\frac{k}{n-k}}&\text{if $k\geq\frac{2-\sqrt 2}{4}\cdot n$}
        \end{cases}.
    \]
    Figure \ref{fig:cauchy_estimate} compares for $n=1\,000$ the two upper bounds we have for $|\Dnka nka|$ on a logarithmic scale: the binomial coefficient $\binom nk$ in red, and the bound $B_{R,n,k}$ with the optimally chosen $R=R_{n,k}$ in blue. The $x$-axis represents the values for $k$, while the $y$-axis represents the binary logarithm of the two bounds. In case $|k-n/2|\leq\sqrt{2}/4\cdot n$, it can be observed that the Cauchy estimate yields particularly good bounds compared to the binomial coefficients. In fact, in this case, we get:
    \[
        \Dnka nka\leq\left(\frac{\sqrt 2 n}{n-k}\right)^{n/2}\cdot\left(\frac{n-k}{k}\right)^{k/2}.
    \]

>>>>

Another immediate case for zero coefficients is the following:
\begin{Prop}
    If $p=q$ and $k$ is odd, then $\Dnka nka=0=\Dnka n{n-k}a$.
\end{Prop}

\begin{proof}
    If $p=q$, we have $P_a(z)=(z^4-6z^2+1)^p\cdot(z^2+1)^r$, which can be seen as a polynomial in $z^2$. Thus, the coefficient $\Dnka nka$ of $z^k$ for odd $k$ must be zero in $P_a(z)$. It follows that also $\Dnka n{n-k}a=0$ by Property \ref{prop:symmetry}.
\end{proof}

@@

With this, we can get more cases in which $\Dnka nka=0$:

\begin{Prop}\mbox{}
    \begin{enumerate}
        \item If $n=16m$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+1}\}$ for integers $m,s\geq 0$, where $\ell_s=s(s-1)$, then $\Dnka n2a=0=\Dnka n{k-2}a$.
        \item If $n=16m+2$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+1}\}$ for integers $m,s\geq 0$, where $\ell_s=\left(6s^2+6s+(-1)^s(2s+1)-1\right)/8$, then $\Dnka n3a=0=\Dnka n{k-3}a$.
        \item If $n=16m+4$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+1}\}$ for integers $m,s\geq 0$, where $\ell_s=s^2$, then $\Dnka n2a=0=\Dnka n{k-2}a$.
        \item If $n=16m+6$ and $\{p,q\}=\{m+\ell_s,m+\ell_{s+1}\}$ for integers $m,s\geq 0$, where $\ell_s=\left(6s^2+6s-(-1)^s(2s+1)+1\right)/8$, then $\Dnka n3a=0=\Dnka n{k-3}a$.
    \end{enumerate}
\end{Prop}

\begin{proof}
    It is enough to use the expressions from Table \ref{tab:Dnka_small_k}, and replace $p$, $q$ and $r$ by their respective values. For instance, for the case $n=16m$, we replace $p$, $q$ and $r$ by $m+s(s-1)$, $m+s(s+1)$ and $6m-2s^2$ in the expression $\Dnka n2a=2(p-q)^2-3(p+q)+r$, which yields $\Dnka n2a=0$.
\end{proof}

\begin{remark}
    There are still instances where $\Dnka nka=0$ which have not been described by the above. For instance, we have $\Dnka{34}4a=0$ if $\{p,q\}=\{1,2\}$.
\end{remark}

@@

\begin{remark}
    We can even go ahead and choose $R=R_{n,k}$ in terms of $n$ and $k$, in such a way that the upper bound of $B_{R,n,k}=(M_R)^{n/2}/R^k$ is minimized. To do this, consider any $1\leq k\leq n-1$. We can actually assume that $k\leq n/2$: if $k>n/2$, replace it by $n-k$ (recall that $|\Dnka nka|=|\Dnka n{n-k}a|$ by Property \ref{prop:symmetry}). One can show that $B_{R,n,k}$ is minimal for the following choice of $R=R_{n,k}$:
    \[
        R_{n,k}=\begin{cases}
            \frac{n-2k-\sqrt{2(n-2k)^2-n^2}}{2(n-k)}&\text{if $k\leq\frac{2-\sqrt 2}{4}\cdot n$}\\
            \sqrt{\frac{k}{n-k}}&\text{if $k\geq\frac{2-\sqrt 2}{4}\cdot n$}
        \end{cases}.
    \]
    Figure \ref{fig:cauchy_estimate} compares for $n=1\,000$ the two upper bounds we have for $|\Dnka nka|$ on a logarithmic scale: the binomial coefficient $\binom nk$ in red, and the bound $B_{R,n,k}$ with the optimally chosen $R=R_{n,k}$ in blue. The $x$-axis represents the values for $k$, while the $y$-axis represents the binary logarithm of the two bounds. In case $|k-n/2|\leq\sqrt{2}/4\cdot n$, it can be observed that the Cauchy estimate yields particularly good bounds compared to the binomial coefficients. In fact, in this case, we get:
    \[
        |\Dnka nka|\leq\left(\frac{\sqrt 2 n}{n-k}\right)^{n/2}\cdot\left(\frac{n-k}{k}\right)^{k/2}.
    \]
